\documentclass[11pt, a4paper, twoside]{report}
\usepackage[T1]{fontenc}
\usepackage{amsmath,empheq}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage{placeins}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage[font=scriptsize, labelfont=bf]{caption}

\begin{document}

\begingroup  
  \begin{center}
  \LARGE \textit{Best practice / SOP something programming for "CaMo"}\\[1.5em]
  \large Jonas van den Brink \& Aslak Wigdahl Bergersen \\
  \end{center}
\endgroup

\section*{Version control systems}
Git combined with CI Travis provides a strong tool.

A small introduction to git, but refer to other documents for more extensive introductions.

Go through some of the most common mistakes: how to fix them and other solutions, e.g. large files.

Efficient collaboration with others.

How to add an SSH key for efficient use.

Questions:
Can CI Travis be in integrated with Bitbucket? It is easy with GitHub.\\
Is it easy to port a repository from GitHub to Bitbucket?


\section*{Coding style}
Some basics, refer to PEP8 or similar for more. Definitely need some input from Min.


\section*{Documentation}
Standard docstrings etc.
"Read the docs" as default?


\section*{How to structure a program}
Should this be included? Is closely related to testing.


\section*{HPC}
Storing data on GoogleDrive (from email)


\section*{Reproducibility}
Reading arguments from command line with argParse / parsing a file to ensure reproducibility
and the possibility to go back to old simulation.
Have an actual reproducibility test against some reference data.

\section*{Testing}
pytest?

How to use tests as a debugging tool, interactive session.


\section*{Debugging/how to work efficiently}
IPython embed + pytest?
Learn a text editor


\end{document}
